The Argennon Virtual Machine

### 2021-03-29 tex/avm.tex
Update README.md
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

    \begin{itemize}
        \item The ZK-EDB contains a mapping from a set of keys to a set of values.
        \item Every state of the database has a commitment \(C\).
        \item The ZK-EDB has a method \((D, p) = get(x)\), where \(x\) is a key and \(D\) is the associated data
        with \(x\), and \(p\) is a proof.
        \item A user can use \(C\) and \(p\) to verify that \(D\) is really associated with \(x\), and \(D\) is not
        altered. Consequently, a user who can obtain \(C\) from a trusted source does not need to trust the ZK-EDB.
        \item Having \(p\) and \(C\) a user can compute the commitment \(C'\) for the database in which \(D'\) is
        associated with \(x\) instead of \(D\).
    \end{itemize}

@@

    \note{Validators do not need to write the modified pages back to ZK-EDB servers. ZK-EDBs will receive the new
    block, and they will update their database by emulating the AVM execution.}

@@

    The consensus protocol of Argennon is similar to Algorand with a few minor improvements.

>>>>

    \begin{itemize}
        \item The ZK-EDB contains a mapping from a set of keys to a set of values.
        \item Every state of the database has a commitment \(C\).
        \item The ZK-EDB has a method \((D, p) = get(x)\), where \(x\) is a key and \(D\) is the associated data
        with \(x\), and \(p\) is a proof.
        \item A user can use \(C\) and \(p\) to verify that \(D\) is really associated with \(x\), and \(D\) is not
        altered. Consequently, a user who can obtain \(C\) from a trusted source does not need to trust the ZK-EDB\@.
        \item Having \(p\) and \(C\) a user can compute the commitment \(C'\) for the database in which \(D'\) is
        associated with \(x\) instead of \(D\).
    \end{itemize}

@@

    \note{Validators do not need to write the modified pages back to ZK-EDB servers. ZK-EDB servers will receive the new
    block, and they will update their database by emulating the AVM execution.}

    \note{It will be a randomized proof of stake which is under development....}

@@
